---
title: "Regression Analysis"
author: "Team 5"
date:  "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    fig_width: 10
    fig_height: 6
---

```{=html}
<style>

table {
  border-collapse: collapse;
  width: 100%;
}

th, td {
  padding: 8px;
  text-align: left;
  border-bottom: 1.5px solid #ddd;
}
p {
  padding: 15px 10px 15px 10px;;
}

body {
  color: #0f1217;
  font-family: Calibri;
  font-size: 14pt;
  background-color: #f2f2f2;
}

h1 {
  color: #003d99;
  font-family: Trebuchet MS;
  font-size: 20pt;
  padding: 5px 10px 5px 10px;
}

pre {
  color: #708090;
  background-color: #f3f2ff;
}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", echo = TRUE)
```
```{r loading_data, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(ggplot2)
library(tidyr)
library(broom)
library(car)
library(knitr)
library(table1)
library(kableExtra)
library(scales)
library(pander)

ListingsCovid <- read.csv("../../gen/temp/merged_data.csv")
ListingsCovid$room_type <- as.factor(ListingsCovid$room_type)
```

# Summary of the dataset

Hi there, welcome to our regression analysis dataset (`ListingsCovid`), which consists of 14 variables and captures 265 observations in total! To get a clear picture of our dataset, the following statistical summary of key variables used to carry out the regression analysis is provided. Also, the variables are filtered according to countries.

```{r statistics_summary, include = FALSE, echo = FALSE}
table1::label(ListingsCovid$room_type) <- "Room Types"
table1::label(ListingsCovid$log_price) <- "Average Price(log)"
table1::label(ListingsCovid$availability_365) <- "Availability"
table1::label(ListingsCovid$number_of_reviews_ltm) <-
  "New Reviews per Quarter"
table1::label(ListingsCovid$reviews_per_month) <- "Monthly Reviews"
table1::label(ListingsCovid$log_weekly_count) <-
  "Weekly Covid Cases(log)"

overview_1 <-
  table1::table1(
    ~ room_type + log_price + availability_365 + number_of_reviews_ltm + reviews_per_month +
      log_weekly_count | country_code,
    data = ListingsCovid
  )
```

```{r loading statistics summary table, echo =FALSE}
t1kable(overview_1) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14)
```

# Histogram of average price

The histogram below indicates the distribution of our dependent variable -- average price(log). Overall, you can see how many times an average price range happens within the period of 2020-2021. Most data points are clustered on the right side of the histogram; indicating that average price (log) does not follow a normal distribution.

```{r distribution of price by country, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid, aes(log_price)) +
  geom_histogram(
    aes(y = ..density..),
    binwidth = 0.3,
    color = "black",
    fill = "#7DA7CA"
  ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(ListingsCovid$log_price),
      sd = sd(ListingsCovid$log_price)
    ),
    col = "#1C1103",
    size = 0.75
  ) +
  labs(x = "Average Price(log)", y = "Frequency")
```

# Scatterplot of average price vs weekly COVID-19 cases

The following scatterplot indicates whether we could determine a relationship between the average price and weekly COVID-19 cases. The results show that there is no correlation between the two variables; thus, it can be said that the weekly COVID-19 cases are irrelevant to the average price.

```{r echo = FALSE, warning = FALSE}
my_color <- "#7DA7CA"
ggplot(ListingsCovid,
       aes(x = log_weekly_count, y = log_price)) +
  geom_smooth(
    color= "black",
    size = 0.3,
    method = "glm",
    formula = y ~ x,
    method.args = list(family = gaussian(link = 'log'))
  ) +
  geom_point(color = my_color) +
  labs(y = "Average price(log)", x = "Weekly COVID-19 cases(log)")
```

# Scatterplot of average price vs weekly COVID-19 cases by country

Since the previous scatterplot shows no correlation between the average price and weekly COVID-19 cases, we decided to investigate whether the country may affect the results. The finding from the second scatterplot is as follows: the correlations do differ per country -- showing either a positive or negative linear relationship between the two variables, while still, quite a few countries such as the Netherlands, Germany, and Austria show no correlation.

```{r Price per weekly COVID-19 cases by Country, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid,
       aes(
         x = log_weekly_count,
         y = log_price,
         color = country_code,
         digits = 0
       )) +
  geom_point() +
  geom_smooth(
    color = "black",
    size = 0.3,
    method = "glm",
    formula = y ~ x,
    method.args = list(family = gaussian(link = 'log'))
  ) +
  labs(title = "Price per weekly COVID-19 cases by country") +
  facet_wrap( ~ country_code) + labs(y = "Average price(log)", x = "Weekly COVID-19 cases(log)", color = "Country")
```

# Model 1: Simple regression

Before we get into the multiple regression model and add other characteristics to further improve the model, we carried out a simple regression with the dependent variable as average price (log) and independent variable as weekly COVID-19 cases to estimate how the average price changes as weekly COVID-19 cases changes. According to the results,`log_weekly_count` is significant at (p< 0.01). Nevertheless, the R square is quite small, indicating a poor relationship between model 1 and the weekly COVID-19 cases.

___Note___: at first we log both the dependent and independent variables; however,since the weekly COVID cases appear to be more significant without log, we simply use log only on our dependent variable `log_price`.


```{r Model 1: Simple Regression, echo = FALSE, warning = FALSE}
regression1 <- lm(log_price ~ weekly_count, ListingsCovid)
pander(summary(regression1), justify = c("left", "center", "center", "center", "center"))
```

# Model 2: Multiple Regression

Now for the multiple regression, our choice of added variables chiefly depends on which variables improved the R square and overall the model. In comparison to the simple regression model, the R square in Multiple Regression shows that model fits better to our observations!


```{r Model 2:Multi Regression, echo = FALSE, warning = FALSE}
regression2 <- lm(
  log_price ~ weekly_count +
    room_type + minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)

pander(summary(regression2), justify = c("left", "center", "center", "center", "center"))
```

In terms of multicollinearity, all analysed variables have a GVIF below 10. According to the rule of thumb, there is no problem with multicollinearity for any of the variables.

```{r checking multicollinearity of Model 2, echo = FALSE, warning = FALSE}
ListingsCovid_lm2 <- lm(
  log_price ~ log_weekly_count +
    room_type + minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)
vif(ListingsCovid_lm2)%>% kable(caption = "*Model 2: Checking Multicollinearity*")
```

As for heteroskedasticity, the residuals in model 2 have an unequal variance across all the independent variables; overall indicating heteroskedasticity.

```{r Model 2 Heteroskedasticity, echo=FALSE, results='asis', message = FALSE, error = FALSE, warning= FALSE}
my_color <- "#7DA7CA"
residuals_lm2 <- ListingsCovid_lm2$residuals
ggplot(ListingsCovid, aes(x = log_weekly_count, y = residuals_lm2)) + geom_point(color = my_color) + geom_smooth(
  color = "black",
  method = "glm",
  formula = y ~ x,
  size = 0.5
) + labs(y = "Residuals", x = "Weekly Covid count", title = "Model 2: Checking Heteroskedasticity") + theme(plot.title = element_text(
  color = "black",
  size = 14,
  hjust = 0.5,
  face = "italic"
))
```

# Model 3: Regression with added interactions

We have added the interaction between weekly_count and room_type to model 2 to check if it would improve the model fit. By comparing the R squared from model 2 and model 3, it is evident that the the R squared has barely increased.

```{r Model 3 Regression Analysis, echo = FALSE, warning = FALSE}
regression3 <- lm(
  log_price ~ weekly_count * room_type +
    minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)
pander(summary(regression3), justify = c("left", "center", "center", "center", "center"))
```

The variable minimum_nights has the lowest GVIF, so it has the weakest correlation. Whereas,the highest is for the interaction between weekly_count and room_type. Interaction terms naturally produce higher multicollinearity. All analysed variables have a GVIF below 10. According to the rule of thumb,there is no problem with multicollinearity for any of the variables.

```{r Model 3: Checking multicollinearity, echo = FALSE, warning = FALSE}
ListingsCovid_lm3 <- lm(
  log_price ~ weekly_count * room_type +
    minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)
vif(ListingsCovid_lm3) %>% kable(caption = "*Model 3: Checking multicollinearity*")
```

The residuals in model 3 have an unequal variance across all the independent variables, indicating heteroskedasticity.

```{r checking heteroskedasticity of Model 3, echo = FALSE, warning = FALSE}
my_color <- "#7DA7CA"

residuals_lm3 <- ListingsCovid_lm3$residuals
ggplot(ListingsCovid, aes(x = log_weekly_count, y = residuals_lm3)) + geom_point(color = my_color) + geom_smooth(
  color = "black",
  method = "glm",
  formula = y ~ x,
  size = 0.5
) + labs(y = "Residuals", x = "Weekly Covid count", title = "Model 3: Checking Heteroskedasticity") + theme(
  plot.title = element_text(
    color = "black",
    size = 14,
    hjust = 0.5,
    face = "italic"
  ))
```

# Conclusion
To conclude, the number of COVID-19 cases affect Airbnb prices differently per country. Since the multicollinearity and heteroskedasticity of model 2 and model 3 yield the same conclusion, we look mainly at the model fit to determine the best model, which is model 3.



