---
title: "Airbnb Regression Analysis"
author: "Team 5"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{=html}
<style>
body {
  color: #444333;
  font-family: Calibri;
  font-size: 14pt;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", echo = TRUE)
```

```{r loading_data, include = FALSE, echo = FALSE}

library(dplyr)
library(tidyverse)
library(readr)
library(ggplot2)
library(tidyr)
library(broom)
library(car)
library(knitr)
library(table1)
library(kableExtra)
library(scales)
ListingsCovid <- read.csv("../../gen/temp/merged_data.csv")
ListingsCovid$room_type <- as.factor(ListingsCovid$room_type)
```

### Summary of the Data set

Hi there, welcome to our Regression Analysis data set,`ListingsCovid`, which consist of 13 variables and captures 252 observations in total! To get a brief overview of our data set, the following is a statistics summary of key variables used to carry out the regression analysis. The variables are segmented according to countries.

```{r statistics_summary, include = FALSE, echo = FALSE}
table1::label(ListingsCovid$room_type)<-"Room Types"
table1::label(ListingsCovid$log_price) <-"Average Price(log)"
table1::label(ListingsCovid$availability_365) <-"Availability"
table1::label(ListingsCovid$number_of_reviews_ltm)<-"New Reviews per Quarter"
table1::label(ListingsCovid$reviews_per_month)<-"Monthly Reviews"
table1::label(ListingsCovid$weekly_count) <- "Weekly Covid Cases"

overview_1 <- table1::table1(~ room_type + log_price + availability_365 + number_of_reviews_ltm + reviews_per_month+weekly_count|country_code, data = ListingsCovid)
```

```{r loading statistics summary table, echo =FALSE}
t1kable(overview_1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 11)
```

### Histogram of Average Price(log)

The histogram below,shows the distribution of average price (log). The majority of data points are clustered on the right side of the histogram.Also there are quite a few outliers is data set.

```{r distribution of price by country, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid, aes(log_price)) + geom_histogram(binwidth = 0.3, color="black", fill= "#FF5A60")+ labs(x = "Average Price (log)", y = "Frequency")

```

### Scatter-plot of Average Price (log) per weekly Covid-19 cases

The scatter plot shows.....

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r echo = FALSE, warning = FALSE}
ggplot(ListingsCovid,
       aes(x = weekly_count, y = avg_price, color = country_code)) +
  geom_point() + labs(y = "Average price(log)", x = "Weekly Covid count(log)", color = "Country")+ scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),labels = trans_format("log10", math_format(10^.x)))+ scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x)))
```

### Scatter-plot of Average Price (log) and weekly Covid-19 cases by country 

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r Price per weekly count by country code, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid,
       aes(x = weekly_count, y = avg_price, color = country_code, digits=0))+ scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),labels = trans_format("log10", math_format(10^.x)))+
  geom_point()+
  labs(title = "Price per weekly Covid count by country") +
  facet_wrap(~ country_code) + labs(y = "Average price(log)", x = "Weekly Covid count", color = "Country")
```

### Model 1: Simple regression with the dependent variable as Average Price (log) and independent variable as weekly Covid-19 cases.

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r simple regression, echo = FALSE, warning = FALSE}

lm(log_price ~ weekly_count,ListingsCovid)%>%
  tidy() %>%
  kable(caption = "*Model 1: Simple Regression* ($n=252$)",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "**Estimate**", "**Std. Error**", "**T value**", "**p.value**"),
    digits = c(0, 4, 4, 2, 4)
  )
```

### Model 2: Multiple Regression with other characteristics of listings.

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r Regression Analysis Model 1, echo = FALSE, warning = FALSE}
  lm(log_price ~ weekly_count +
      room_type + minimum_nights +
      reviews_per_month +
      number_of_reviews_ltm +
      availability_365,
    ListingsCovid
  )%>%
  tidy() %>%
  kable(
    caption = "*Model 2: Multi Regression*($n=252$)",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "Estimate", "Std. Error", "T value", "p.value"),
    digits = c(0, 4, 4, 2, 4)
  )
```

### Model 2: Checking for Multicollinearity.

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r checking multicollinearity of Model 1, echo = FALSE, warning = FALSE}
ListingsCovid_lm1 <- lm(log_price ~ weekly_count +
                        room_type + minimum_nights +
                        reviews_per_month +
                        number_of_reviews_ltm +
                        availability_365, ListingsCovid)
vif(ListingsCovid_lm1) %>% kable(caption = "*Model 2: checking multicollinearity*")

```

### Model 2: Check for Heteroskedasticity.

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r checking heteroskedasticity of Model 1, echo = FALSE, warning = FALSE}
my_color <- "#FF5A60"

residuals_lm1 <- ListingsCovid_lm1$residuals
ggplot(ListingsCovid, aes(x = weekly_count, y = residuals_lm1)) + geom_point( color = my_color)+ labs(y = "Average price(log)", x = "Weekly Covid count", title= "Heteroskedasticity of model 2") + theme(plot.title = element_text(color="black", size=14, hjust = 0.5,face= "italic"))
```

### Model 3: Regression with added interactions between weekly Covid-19 cases and room types.

blah According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighborhood compared to traditional hotels.

```{r Regression Analysis Model 2, echo = FALSE, warning = FALSE}
 lm(log_price ~ weekly_count * room_type +
    minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)%>%
  tidy() %>%
  kable(
    caption = "_Model 3: Muliple Regression with Interactions_",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "Estimate", "Std. Error", "T value", "p.value"),
    digits = c(0, 4, 4, 2, 4)
  )
```

### Model 3: Checking for Multicollinearity

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighborhood compared to traditional hotels.

```{r checking multicollinearity of Model 3, echo = FALSE, warning = FALSE}
ListingsCovid_lm2 <-lm(log_price ~ weekly_count * room_type +
                         minimum_nights +
                         reviews_per_month +
                         number_of_reviews_ltm +
                         availability_365,
                       ListingsCovid)
vif(ListingsCovid_lm2)%>% kable(caption = "*Model 3: checking multicollinearity*")
```

### Model 3: Checking for Heteroskedasticity.

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r checking heteroskedasticity of Model 2, echo = FALSE, warning = FALSE}
residuals_lm2 <- ListingsCovid_lm2$residuals
ggplot(ListingsCovid, aes(x = weekly_count, y = residuals_lm2)) + geom_point(color = my_color) + labs(y = "Average price(log)", x = "Weekly Covid count", title= "Model 3: checking heteroskedasticity") + theme(plot.title = element_text(color="black", size=14, hjust = 0.5,face="italic"))
```

### Conclusion

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighborhood compared to traditional hotels.

### References

Statista. (2021). Least affordable cities for backpacking in Europe for 2020, by daily price index (in U.S. dollars). Retrieved from <https://www.statista.com/statistics/696870/most-expensive-cities-for-backpacking-europe/>

Statista. (2021). Cheapest cities to visit in Europe as of December 2021, by daily price. Retrieved from <https://www.statista.com/statistics/696725/most-affordable-cities-for-backpacking-europe/>
