---
title: "Data Analysis"
author: "Team 5"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

<style>
body {
  color: #444444;
  font-family: Calibri;
  font-size: 14pt;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", echo = TRUE)
```

```{r loading_data, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(ggplot2)
library(tidyr)
library(car)
library(knitr)
library(table1)
library(kableExtra)
ListingsCovid <- read.csv("../../gen/temp/merged_data.csv")

```

### Summary of the Merged data

`merged_data` contains listings of 17 analyzed European cities. It captures around 200,000 observations in total, and not every city has the same number of listings as one another. Below is an overview of the first few rows and columns of the `merged_data`


### Histogram of avg_price(both with and without log function)

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.



```{r distribution of price by country, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid, aes(avg_price)) + geom_histogram(binwidth = 0.1) + scale_x_log10() + labs(x = "Log of average price", y = "Frequency")

```

### Scatterplot of Price per weekly count


According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.



```{r echo = FALSE, warning = FALSE}
ggplot(ListingsCovid,
       aes(x = weekly_count, y = avg_price, color = country_code)) +
  geom_point() +
  scale_y_log10()
```

### Scatterplot of Price per weekly count by country code

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r Price per weekly count by country code, echo = FALSE, warning = FALSE}
ggplot(ListingsCovid,
       aes(x = weekly_count, y = avg_price, color = country_code)) +
  geom_point() +
  scale_y_log10() +
  labs(title = "Price per weekly count by country code") +
  facet_wrap(~ country_code)
```

### Simple regression with DV Log avg_price and IV weekly_count


According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.



```{r simple regression, echo = FALSE, warning = FALSE}

lm(log_price ~ weekly_count, ListingsCovid)%>%
  tidy () %>%
  kable(
    caption = "**Model 1: Simple Regression** ($n=252$)",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "**Estimate**", "**Std. Error**", "**T value**", "**p.value**"),
    digits = c(0, 4, 4, 2, 4)
  )
```

### Regression with other characteristics of listings


According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.


```{r Regression Analysis Model 1, echo = FALSE, warning = FALSE}
  lm(log_price ~ weekly_count +
      room_type + minimum_nights +
      reviews_per_month +
      number_of_reviews_ltm +
      availability_365,
    ListingsCovid
  )%>%
  tidy() %>%
  kable(
    caption = "Model 2: Multi Regression",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "Estimate", "Std. Error", "T value", "p.value"),
    digits = c(0, 4, 4, 2, 4)
  )
```


According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.


```{r checking multicollinearity of Model 1, echo = FALSE, warning = FALSE}
ListingsCovid_lm1 <- lm(log_price ~ weekly_count +
                        room_type + minimum_nights +
                        reviews_per_month +
                        number_of_reviews_ltm +
                        availability_365, ListingsCovid)
vif(ListingsCovid_lm1) %>% kable()

```


According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.


```{r checking heteroskedasticity of Model 1, echo = FALSE, warning = FALSE}
residuals_lm1 <- ListingsCovid_lm1$residuals
ggplot(ListingsCovid, aes(x = weekly_count, y = residuals_lm1)) + geom_point()
```

### Regression with added interactions between weekly count and room type

blah According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r Regression Analysis Model 2, echo = FALSE, warning = FALSE}
 lm(log_price ~ weekly_count * room_type +
    minimum_nights +
    reviews_per_month +
    number_of_reviews_ltm +
    availability_365,
  ListingsCovid
)%>%
  tidy() %>%
  kable(
    caption = "Model 3: Muliple Regression with Interactions",
    align = c("l", "c", "c", "c", "c"),
    col.names = c(" ", "Estimate", "Std. Error", "T value", "p.value"),
    digits = c(0, 4, 4, 2, 4)
  )
```

### check multicollinearity

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r checking multicollinearity of Model 2, echo = FALSE, warning = FALSE}
ListingsCovid_lm2 <-lm(log_price ~ weekly_count * room_type +
                         minimum_nights +
                         reviews_per_month +
                         number_of_reviews_ltm +
                         availability_365,
                       ListingsCovid)
vif(ListingsCovid_lm2)%>% kable()
```
### Check heteroskedasticity

According to the statistics summary, entire home/apartment accumulates more than half of the observations. This tendency also appears across listings of each city. Taking up the second most offered type of room is private room. What we could take on from here is that the Airbnb landscape in European market values privacy and personal comfort but at the same time the guests can stay close to local neighbourhood compared to traditional hotels.

```{r checking heteroskedasticity of Model 2, echo = FALSE, warning = FALSE}
residuals_lm2 <- ListingsCovid_lm2$residuals
ggplot(ListingsCovid, aes(x = weekly_count, y = residuals_lm2)) + geom_point()
```

